\chapter{}

\lettrine{A}{fter} two weeks of walking up and down, Aryan finally set up his
new home on the hills. He bought only those items that were necessary. He bought
a foldable table and a plastic chair to work on his laptop and to have meals. He bought
basic cutlery, crockery, and utensils to store grains, vegetables, and to
cook food. He made a solar cooker to boil rice and vegetables. He set up a
wood-fired stove with a few stones and collected firewood from nearby trees to
light a fire. He covered the main door and windows with curtains for privacy. He bought
mattresses and pillows for sleeping.

He attached two solar panels on the roof to generate electricity during the
day. He bought batteries to store the generated power, so that he could
use a couple of LED lamps during the night. He could also charge his
laptop and cell phone when needed. He dug a pit and installed a
compostable toilet. He bathed and washed clothes in the nearby stream. The
stream also provided him with abundant fresh water—he boiled some for drinking.

He visited shops on the new walking route to buy rice, vegetables, and other essential
supplies. He started to grow vegetables around his new home and picked many fruits
from the surrounding trees. He stocked up on as many supplies as possible and tried his
best to reduce his reliance on the outside world—he didn't want to attract
unnecessary attention walking in and out of the forest regularly.

He now focused his attention on practising archery and making plans for his
attack. With a weak cellular signal, he was able to connect to 2G internet. He
bought newspapers and magazines whenever he went out. He kept track of all the
movements of the minister, both online and offline. He bought books on archery to
learn more about the attack strategies employed by archers in ancient times.

After a few weeks, the anticipated moment finally arrived—the minister was
coming to Tirupati on his birthday, and newspapers and websites featured the news
prominently. He calculated that the minister's security cover would be minimal,
and hence formed a plan to kill the minister while he was on his way down. However,
he did not expect the turn of events that actually unfolded.