\chapter{}

\lettrine{T}{irupati} is a historic town where the temple of Lord Venkateswara, an  
incarnation of Lord Vishnu, is located. Though the temple is on the hills, the town itself is split into two parts: Tirupati town, located below the hills and Tirumala town, located over the hills.

Since the town is an important pilgrimage centre, millions of Hindu devotees visit the 
temple every year. The queue for darshan (having a glimpse of the statue of the God) is
generally long, and on average, a devotee spends many hours waiting for
it. The town is swarmed by pilgrims throughout the year, and is well-connected
through air, train, and bus services.

Tirumala is situated at the top of the hills, which is reachable by road using both cars and
buses. There is another way to reach the top of the hills from the town,
which thousands of people use regularly—by walking through the hills. Before
the roads were constructed, this route was the only way to reach Tirumala. For an average
person, it takes four to six hours to climb up the hills on foot.

The walking route is covered with steps, cemented pathways, and a roof, from the bottom
of the hill to the top. Since people walk up and down during the nights too, the
route has been electrified. There are various shops located on the sides of the
stairs. If something is unavailable, shopkeepers shuttle between Tirupati town
and their hill-top shops to bring it on request. On his first visit, Aryan
noticed all these things and was convinced that his supplies, groceries,
and vegetables could easily be procured from the vendors on this route. He didn't
have to go to either Tirupati town or Tirumala town for that. This was important for
him to evade the police.

Not many people know that there were other walking routes that were used to
traverse the hill, in ancient times, but mostly abandoned now. One such
route intersected with the present walking route. Aryan had identified it using
Google Maps, but he couldn't locate it initially. With the help of his
smartphone and GPS tracker, he pinpointed the ancient route that was few hundred
meters away from the current route, winding through the trees.

Aryan immediately set off to explore the ancient route, which led him deeper
into the jungle. Initially he was intimidated by the vast expanse of nature, but
as he moved deeper into her lap, he was overwhelmed with joy. He felt as if he had finally come home.

As he was exploring, he was looking for two things—a place to live and a fresh water 
source. Local people had informed him about a stream that flowed from the top of the 
mountain and cascaded into a waterfall below. With the help of Google Earth, he identified
that this stream intersected with the old unused route, he was currently walking on.
His goal was to reach that exact point.

After walking downhill for many hundred meters on the old unused route, Aryan found
the stream. This was the fresh water source he was searching for. The stream
crossed his path and the wooden bridge that once spanned it, now lay broken. He
couldn't cross the bridge, but he didn't want to cross it anyway.

He had to find a place to live just before the stream. He was
looking for a cave or shelter and luckily, he found an old traveller's rest
house. This one-storey stone structure, possibly built to enable weary travellers on
foot to rest for sometime during ancient times, offered a perfect place for
him to stay safely in this remote location, amidst the hills' forests.

The rest house was built over a raised platform with a roof resting on pillars.
A thick stone wall made of large grey stones enclosed almost all four sides
except for the entrance which remained open, without a door. There were two
steps leading into the house. There were open windows in the middle of all the
three side walls for light and ventilation. Since the building was old and
unused for a long time, it was partially covered with vegetation, and he found a
few bats hanging from the roof.

He started cleaning the house and soon it looked more liveable. This was more
than what he had hoped to find in this remote location. It was the perfect home
he was searching for!

As darkness was approaching fast, Aryan retraced his steps along the old
unused route and reached the new one. He quickly blended in with the people walking there.
After walking down the stairs for a couple of hours, he reached his hotel room and took a 
long nap. He had a lot of planning and shopping to do over the next couple of days.