\chapter{}

\lettrine{T}{he} General Election results were announced soon after. Even though the ruling
party won the elections and formed the Government once again, Guru lost his
constituency. He was no more a Minister. A few crimes didn't go well with people
and murder was chief among them—people didn't vote for someone else, but they
voted against him. The old cabinet was largely retained as such, without Guru
(who lost the elections). The Conventional Energy and Renewable Energy
portfolios were consolidated together under a single Ministry and was given to
another minister—Nadeem. What Guru wanted to achieve all these days was
finally accomplished, but he was not there to enjoy its fruits.

Nadeem got a huge bounty—almost on a platter. Even though Nadeem was excited
initially, his enthusiasm waned soon after. His contacts and well-wishers
indicated to him that even though the old Minister, Guru, was no longer
in-charge, his hold, over important executives of the department, was still very
strong. Nadeem hoped things would get better with time, but found evidence to
the contrary—the old Minister was working very hard to strengthen his grip
over the department. Guru was determined to milk the cow as long as possible.
Nadeem had to stop him now or this may continue forever.

Having worked in two different ministries before, Nadeem was no stranger to
power politics and games. But Guru, the old Minister, was holding on like a
leech. He had a powerful grip over the key executives of the department. The
executives were scared to take a stand against the interests of Guru. Even
though Nadeem knew he would win in the long-run, Guru's actions would only cause
unnecessary delays and conflicts which could prove expensive.

Someone mentioned to Nadeem about Aryan and Divya and the case against them
instituted by Guru. Nadeem's curiosity was piqued, and he wanted to know more. He
ventured deeper and used his influence to gather all the critical information
related to the case. The more information he gathered, the more he was convinced
that it could be used against Guru. Though Nadeem didn't believe in using
violence to eliminate people, he didn't have any problem if someone else wanted
to use it. Violence or non-violence, Guru had to be eliminated from the scene.
Nadeem was determined to use every possible resource to muster against him.

Two weeks later, Aryan and Divya were informed that Guru had lost the elections.
The new Minister appointed in his place, Nadeem, wanted to meet them. Aryan
couldn't guess what the new Minister might want from them. He was ushered into
the interrogation room. Divya was already sitting in one of the chairs, and she
was in a cheerful mood.

“I guess we achieved something—the Minister has lost the elections,” Aryan
said after the Constable who accompanied them left, and smiled at her.

“We achieved more than that,” Divya said and smiled back as the door opened and
the new Minister, Nadeem, walked in.

“I guess you are Aryan and Divya. I am glad to meet you two,” Nadeem said after
the door closed behind him. Both of them looked at him blankly.

Nadeem didn't expect them to trust him immediately. He said, “Oh, don't suspect
me of having any connections with Guru—he is my rival, and he is causing a lot of
trouble. I am here to help you get out of the prison. An industrialist friend
will arrange your release. By tomorrow your bail applications will be processed,
and you'll be free.”

“But why do you want to take us out on bail?” Divya asked.

“Well, both of you are young, and it hurts me to see youth spending precious
years of their life behind bars. I know the case history and I also know you
both are innocent,” Nadeem replied.

Aryan said, “This is not an election rally, and we are not people to be won over
by your sweet talk. Give us the real reason—what do you expect from us?”

“Let's just say,” Nadeem said, “my enemy's enemy is my friend. I understand that
you two have some unfinished business with the Minister, don't you?” He winked
at them. Aryan got the message, smiled within, but kept quiet. Aryan's reaction
indicated to Nadeem that he was eager to utilize this opportunity.

Nadeem continued, “Guru is a powerful man—with or without his Ministry. If he
comes to know that you two are out on bail, he will pursue you. I think you
should go back to your forest house or… whatever you have created in the
hills. That seems like a safe place for now.”

“But the police knows the location of our hide—out in the hills. They arrested
us from there,” Aryan said.

“The police will not interfere with whatever you do this time. While I have
already taken care of their interests in advance, Guru never fulfilled any of
his promises,” Nadeem said.

Aryan and Divya looked at each other.

“I am not lying—I don't have to. As you can see, I've been frank with you—you
can trust me. I hope you'll utilize this opportunity to the fullest. All the
best,” Nadeem said. Before leaving, he gave his cellphone number to them and
asked them to contact him in case they needed any help.