\chapter{}

\lettrine{I}{n India}, people usually become successful politicians because they are the kin
of successful ministers or MLAs, related to or friends of industrialists, or famous
film stars or social activists.

Guru was none of them.

He was the eldest among six siblings. When he was nineteen years old, his
father, a construction labourer, died in an accident. Guru was obliged to quit
his Government College education and join his mother in the construction work
to support his family.

Initially, he was content with the daily wages that were provided. Since his
brothers and sisters were still studying in a government school in Chennai,
they had access to free meals provided by the State. Money earned by Guru and
his mother was sufficient to feed the family in the mornings and at night.
But, the income of the family was not enough to arrange her sisters' marriages.

In India, parents need to provide dowry, usually in the form of gold jewellery
or cash, to get their
daughters married. The value of the dowry determines the status of the groom.
This practice was not prevalent in all communities, but in Guru's case, dowry
was very much a reality. Guru knew that he had to earn considerably more, and that
too in a short period, if he wanted to get his sisters married into
relatively well-to-do families.

Guru was a keen observer of people and noticed that some workers occasionally
died or suffered major health ailments due to the poor safety standards
maintained by construction companies at their sites. The contractor he worked
for was no different—he did not consider spending
on the well-being of labourers to be a good investment.

Guru also noticed that there was no labour union to fight for the
rights of labourers. He formed an informal labour union and started negotiating
with his employer on behalf of the affected families. He tried his best to
secure monetary compensation for the families of labourers who died or suffered
serious ailments due to their strenuous working conditions.

Initially, he faced a lot of opposition from his employer for his attempts to
bring justice to the labourers. He was attacked by thugs hired by his employer,
but he managed to survive the assault. The incident only increased his
determination to fight. His efforts were noticed by other labourers, and he formed
a network of able-bodied labourers to fight any such attacks in the
future.

Unable to take him down by force, his employer relented and offered
monetary compensation to the affected families. This turned Guru into a hero among the
labourers, and he became their saviour. Labourers now consulted him about their problems
concerning company management, and he became their unelected representative.

Guru enjoyed this responsibility and the respect it earned him, but he soon
realized that he was unable to make any money from these endeavours.  What he
did amounted to social service, not business.

Since he had secured the trust of labourers, Guru decided that it was time to
capitalize on that trust. He now negotiated with both parties to strike the best
deal possible—for the employer.  He was paid a handsome commission for these
cost-reduction efforts.  Guru found that he was not only able to make a decent
amount of money, but was also much sought after and thanked by both the
labourers and their employer. Even though he didn't realize it, he was already
learning the art of politics.

“Why should I ask my workers to vote for you? What have you done for our company
over the last few years as a ward councillor?” Guru heard his boss fuming over
the phone as he entered the general manager's cabin. The boss said, “Look at
this Guru—this useless ward councillor won the previous election because I
recommended his name to all our labourers. But, he conveniently forgot us
after that. Now he wants me to canvass for him again. What makes him think that
I will agree to it? I really don't understand. Anyway, what brings you here?”

Guru said, “You called me this morning to discuss the compensation to be
given to—”

His boss interrupted. “Oh, that. You do the best you can. I know you'll have
the company's interest as your topmost priority. Am I right?”

Guru said, “Sir, I have never forgotten it. You know that.”

His boss nodded his head and got into thoughtful contemplation for a few
seconds. He then looked at Guru and said, “Guru, I have an idea—what stops you
from contesting the ward councillor election yourself? I am sure all our workers
will support you. You live in this area, and know almost everybody in
the colony. You should be able to convince people to vote for you. You have a
good name among them. What do you think?”

“But I have never contested an election before, Sir. Besides, I don't
have the money required for campaigning”, Guru replied.

“Don't worry about funds. I'll sponsor your campaign. It's time you stop
slogging as a labourer and start handling bigger responsibilities. A journey of
a thousand kilometres begins with a single step. Go ahead and file your
nomination papers—you have my blessings”. Guru could not refuse these words of
his boss, but didn't anticipate how big that responsibility might become, one
day.

Guru visited the Tirupati Temple for the first time, a day before the election
results were announced. He became nervous and someone suggested he visit the
powerful God of the Seven Hills in Tirupati. Guru boarded the earliest bus to
Tirupati, even though he did not have the habit of visiting temples. Guru needed
some way to overcome his anxiety.

As soon as he reached Tirupati, he walked to Alipiri and then made his way up by
foot instead of taking another bus to reach the Tirumala temple on the hilltop.
He reached the temple at midnight, and he had to wait for twelve hours for the
darshan of the God. Even though the journey was physically exhausting, it
soothed his nerves and helped him shed the mental tension of the previous day.

After coming out of the temple, Guru was much more relaxed. He knew that the
result would have been announced by then. He was tempted to call home, but
instead, he bought food, distributed it among the hungry poor, ate some and
boarded a direct bus to Chennai.

He reached Chennai in the evening and went home directly. When he knocked on the
door, his wife rushed to open it, beamed, and informed him that he had won the
election. He embraced her, looked into her eyes, and said calmly, “I know.”
Thereafter, he made it a point to visit the Tirupati temple at least once a
year.

Thirty-five years have passed since then and Guru has visited the Tirumala
temple much more than 35 times now. Over the visits, he also advanced in his
political career. From being a ward councillor, Guru became a member of the
Legislative Assembly and a state minister, and later, a member of parliament and
a central minister.

During his second term as a central minister he managed to wrest the 'plum'
Ministry of Power portfolio from a rival.  The rival minister, however,
convinced the prime minister to split it into two and became in charge of the
Renewable Energy portfolio.

This was a major setback for Guru as new power projects were about to be
sanctioned to produce power using renewable energy technologies, and additional
funds were released to subsidize the rooftop and commercial solar installations.
The renewable energy projects were completed much faster compared to the
fossil fuel and nuclear-based power plants he was setting up. There were plenty of
business opportunities in the Ministry of Renewable Energy, and all of them were
snatched away from him.

Guru did not take this defeat lightly. Not only was he addicted to money and
power, but he also wanted to be invincible. For the first time, he chose not to
circumvent the roadblocks in his path—he wanted to uproot them, reduce them to
rubble, and trample triumphantly over them, turning them to dust. That, he thought,
would be a fitting reply to his rival.
