\chapter{}

\lettrine{A}{ day} before their scheduled attack, Aryan and Divya travelled
from Tirupati to Chennai in the unreserved compartment of the train. They
started early in the morning and reached Chennai before noon. They had already
booked a hotel near the railway station so that they could check into the hotel 
immediately after they reached Chennai. Aryan picked up a second-hand motorcycle
that he had found on an online classifieds site, after paying the requisite amount
that was already agreed upon with its owner via email. They wanted to use the bike to
reach the guest house and quickly get away from there without anyone's
knowledge. Since the bike was not registered in their name, they figured it would
be difficult to trace its ownership even if someone managed to note down the
number while they were trying to escape.

The East Coast Road, affectionately called the ECR by the locals, is the
entertainment highway of the southern metropolitan city of India—Chennai. The
road, stretching all the way from Chennai to Pondicherry, a former French colony,
is two hundred kilometres long. It is dotted with various entertainment avenues
like theme parks, resorts, beaches, and guest houses. The road has been built
along the beaches of the Bay of Bengal in the eastern coast of India and hence
its name. Flanked by the beach on one side and the IT highway with high-rise
office complexes, on the other, the area around ECR has residential villas and
VIP guest houses.  Guru, the minister, owned a large guest house on one of the
smaller roads connecting the beach and the ECR highway.

Aryan and Divya reached the actual scene of attack and surveyed both the
minister's guest house and the area on the beach from where they would launch
their arrows. Google Maps had reproduced the area fairly accurately, so
they were not in for much of a surprise. They parked their bike on the lane
adjacent to the beach and played in the beach water for some time while
simultaneously surveying the area. As they had expected, there was no one near
the beach. That reassured them that the place would be equally secluded late in the
evening on the following day, when they planned to carry out their attack.

There were two more parallel roads connecting the ECR highway to the beach lane,
about a hundred meters to the left and right of the minister's guest house. They
decided to use one of them—the left one, to park their vehicle and exit out of
the beach after their attack.

The next day, as planned, they came to the same spot at around 6:30 in the evening.
The sun had almost set, but there was enough light for them to position
themselves at the right location on the beach from where they planned to launch
their arrows. They carried two re-curve bows in a large black bag, both remaining
dismantled inside, to be assembled on the spot. The bag concealed the bows
from public view. They also brought some heavy aluminium arrows with
edges deliberately blunted to avoid causing much harm to the people
partying on the terrace of the minister's guest house.

As they had expected, the road leading to the minister's guest house from the
ECR was heavily guarded, and the police were checking people and vehicles
arbitrarily. They went past that road and took the next left turn to reach the
beach. There were no police or security personnel on this road. Aryan parked the bike close
to the beach, and they walked back a hundred meters along the beach lane to reach
their predetermined spot. They sat down on the spot and pretended to talk about
silly things to appear like lovers to anyone who may pass by. They would
wait until 6:55 PM to assemble their bows—by then, it should be
sufficiently dark, making it difficult for anyone to notice their activity.

At 6:40 PM, while they were chatting about some inconsequential things, they saw
a guard approaching them.

“Someone is approaching us. What do we do now?” Divya asked.

“I don't think there is any reason for anyone to suspect us yet. Just keep
talking silly things and pretend we are lovers casually passing time on
the beach,” Aryan said.

In spite of this decision, they were silent, and their hearts were beating fast.
What if the guard finds the bows and arrows? Would they be arrested?

As the guard came closer, they noticed that he was not a police. He was probably
a private security guard working for one of the many villas around the area.

“What are you two doing here?” the guard asked.

Aryan replied, “We are friends. We just came to pass our time on the beach.”

“Are you two college students?” he asked.

“Yes, same college and same class,” Divya replied.

“Show me your college ID cards,” the guard demanded.

“We didn't come directly from college. We went home and then came here. Our
ID cards are at home,” Divya said.

By this time, the guard had noticed the unnaturally long black bag lying next to
them.

“What's in that bag?” he asked.

“That's my cricket bat and stumps kit. I need to hand it over to a friend on my
way back—that's why I brought it,” Aryan said.

“Open the bag, let me see what's inside,” the guard said.

Aryan paused and took a deep breath. There was no way he could show the contents
of that bag to the guard. Not only were they carrying bows and arrows, but they had
also lied to him.

“Why should I show that to you? Do you have a search warrant? Are you a police officer?”
Aryan asked.

The security guard was taken aback for a moment. He then said, “See, this is an
empty beach, and it is not safe for youngsters like you to be roaming around at
this time. It would be better if you two go back home now,” the guard
said.

“But, we came just now,” Divya protested.

“It's OK. We'll go back. Thanks for your concern,” Aryan said, hung the bag over
his shoulders, pulled Divya's hand, and started walking towards their bike.

“What do we do now?” Divya whispered once they reached their bike.

“We couldn't stay there—it would have only increased his suspicion. We'll wait
here for ten minutes and then go back. By that time, I think he will have
left,” Aryan replied.