
\chapter{}

Aryan's mission was to kill the minister who was visiting the mountainous Temple
town of Tirupati. Today was the minister's birthday and he had come for the
blessings of the powerful God over seven hills. Aryan was waiting for this
moment past six months.

Tirupati or Tirumala is a famous Temple town located over the hills in South
India. It has two separate roads (both one-ways) – one for driving over the hill
and the other for coming down. Aryan was waiting for the minister's car to
approach, on the way down.

The downhill road contains some fifty hairpin bends (steep U-turns) to slow down
speeding vehicles. In between the U-Turn was the remnant of the mountain itself.
He was able to climb over this mountainous patch, four meters above the road and
twenty meters before the U-Turn, using a rope. From this elevated position, he
could see all the vehicles approaching the U-Turn. He could also see all the
vehicles moving away from the U-turn if he moved over to the other end, a few
meters behind his current location. Since Aryan was over the mountain (on the
middle of the U-turn) and the road curved around him, both sides of the U-turn
were accessible to him.

Aryan had kept a cluster of nails to puncture the car tires, below him, along
the corner of the road. He had a long stick with which he would push one side of
the cluster of nails to the middle of the road. When the minister's car rode
over it, the tires will - most probably - get punctured. A car with punctured
tires will be difficult to control, especially while negotiating a U-turn, and
there is a good chance that it may topple over the one-and-a-half feet high
perimeter wall along the boundary of the mountain. There was no way anyone
inside the car could survive such a huge fall.

But, there was a good chance that the driver might be able to control the
vehicle, and manage to turn the vehicle successfully around the U-turn. If that
should happen, the car will still have to stop immediately after crossing the
U-turn for replacing the punctured tire. Aryan would use his bow and
poison-soaked arrows to kill the minister, right there. Aryan was a trained
archer - he rarely missed his target.

He was ready for action – he would strike the heart of the heartless minister,
today. The minister had killed his father and hence he will have to pay for it
with his life.

Aryan was suddenly distracted by the rotating lights of an Ambassador car. Why
do some politicians still use Ambassador cars – the question was beyond him. Why
they flashed the rotating lights and blared the siren on their car, was also
beyond him. These things were not going to be of much use in Indian roads and
traffic. It would only help potential killers, like him, to easily identify the
car.

Fortunately, the car was coming alone - without any escort vehicles. There was
another car about fifteen meters in front of the minister's car, but that was a
tourist car. Once it passed, he quickly pushed one end of the cluster of nails
to the middle of the road while the other end still remained in the corner. He
was sure that at least one of the car tires would roll over it.

Not one, but both the tires on the driver's side (right side) rolled over his
nails and were punctured instantly. While the tires were deflating, the car
briefly got out of control and was wobbling on both sides. Somehow, the driver
managed to steer the car around the U-turn and stopped it 15 meters ahead of the
U-turn.

Aryan quickly ran to the other side of the mountainous patch in between the
U-turn – through plants, mud and trees – and noticed the car stop a few meters
ahead of him. The car didn't topple over the mountain, as he had hoped.

Time for Plan B – he removed his bow from his shoulder and took out an arrow
from the pouch tied on his back. The car was clearly visible to him below and
his location gave him the perfect opportunity to strike from close range. He
ducked behind the mud and grass to escape their notice. Aryan wasted no time
getting into striking position with his bow and arrow.

But the minister had to step out of the car, for him to strike.

The driver got out first. He discovered that two wheels were punctured and
informed someone inside. The security guards got down, opened the car's Dicky
and brought out spare wheels. They had two spare wheels! Heck, they were well
prepared for eventualities.

He waited in bated breath for the Minister to get down while the tire was being
changed. All his planning and efforts over the last six months came down to this
very moment. But it seemed he was out of luck today - the minister did not come
out.

After the tires had been replaced, the guard knocked the window on the back door
of the car. The window glass came down and he spoke something to the Minister,
seated inside. At last, the car door opened and the Minister – in his white
shirt and white dhoti – came out to have a look at the tires. Aryan stretched
his bow and tightened his grip on the arrow. He was waiting for the minister to
turn towards him. Aryan probably had only one chance and the arrow had to pierce
through the Minister's heart in the first attempt.

After inspecting the wheels, the Minister turned to face the guards. This was
the moment Aryan was waiting for. The Minister's heart was in his line-of-sight.
He tightened his grip. But before Aryan could release his arrow, the minister
was hit on his shoulder by another arrow.

Aryan's eyes widened and he froze for a moment.

He looked down to check if he had accidentally released his arrow. No, his arrow
was firmly in his hands. Then whose arrow was that? Everyone near the car
panicked. Before Aryan could recover from his shock, the minister quickly
sneaked into his car, removed the arrow, and threw it out of the car's window.
The security guards took their guns out and positioned themselves behind the
car. They started shooting in the direction from where the arrow was launched,
which was about 15 to 20 meters ahead of Aryan's position, on the mountainous
patch above the road.

Aryan heard a loud cry. Probably, someone was hit by a bullet. Who could it be?
Whoever it was, he had to save them. He now fired his arrow on one of the
security guards, which hit the guard's hands. The guard dropped his gun, removed
the arrow from his hands with great effort and winced in pain. Having realized
that there were more archers, possibly all around them, the guards and the
driver got into the car and sped away.

Aryan raced toward the place from where the other arrow was shot and found
someone - dressed in a black shirt and black jeans – lying on the ground. Was
the person all right? Was he already dead? Aryan turned him around to see. It
was not a guy but a girl.
