\chapter{}

\lettrine{A}{ryan}, 21, was studying the final year of his undergraduate course
(Environmental Engineering) in the UK, when he was informed of his father's
death.

Aryan initially believed that his father died due to cardiovascular arrest.
That's what the hospital report said. The moment he landed in New Delhi, he
sought more information about his father's death. People informed him that his
father had fainted in the office and passed away en-route to the hospital. No
one told much and Aryan did not suspect the authenticity of the report.

Few days after his father's final rites, Aryan got a phone call from a stranger.

“Is this Aryan?”

“Yes, who is this?”

"I have something important to tell you. Are you alone now?”

“Yes, but who are you?”

“My name does not matter. I work in your father's office. Your father did not
die due to heart-attack. He was killed - his tea was poisoned.”

“But the hospital report says -”

“That report is false. It was made up on the behest of some key doctors working
there. Actually, they were forced to write the false report.”

“Please reveal your identity – how can I trust you otherwise?”

“I don't have to call you and tell you this, but your father was more than just
a colleague. He… he has helped me a lot in my career.”

“Why don't you inform the police about this?”

“If I do that, I will probably lose my job. Or worse, get killed myself.”

“This sounds more like speculation than reality. Do you have any proof of your
claims? Do you at least know who is the killer?”

“I know who is the killer. Your father was killed by the Petroleum and
Conventional Energy Minister – Guru.”

“Why would he kill my father?”

“Inter-ministerial rivalry. Your father was the right-hand man of the minister
of Renewable Energy. There had been a tussle between the Ministry of Renewable Energy
and the Minister of Petroleum and Conventional Energy for funds. The prime minister
intervened to close the case in favour of the former. This
upset Guru, the rival minister. He planned to eliminate the key people in the
ministry to place his own accomplices inside and indirectly
control the ministry through them.”

“Were more people killed too? Or only my father?”

“Yes. Two more people were killed on the same day - the Renewable Energy
Minister and another key Executive from our Department. All three of them were
killed on the same day, in the same way – by poisoning their tea.”

“If three people, belonging to high positions in the Government died on the same
day, the police or the press should have become suspicious. As far as I know,
there were no police inquiries or press mentions in this case.”

“You should know that it is possible to buy people in India, especially if one
is a Minister. That's the reason I am afraid no action will be taken against the
Minister even if I file a case.”

“What made you suspect murder?”

“Imagine - even though these three people died in different localities, they
were taken to the same Government Hospital that was more than 20 KM away from
their respective localities. Why did they take all three of them to Government
Hospital when there are other good hospitals on the way?”

“But the department people should have carried them – right?”

"Yes, the department people were paid to do this job - the ones who brought the
bodies to the hospital.”

“How can you be sure?”

“These things don't remain hidden for long. People will come to know about it.
Besides, my relative is a doctor in the Government Hospital and she… Don't
you think I am giving you too much information? If you want to know more, talk
to people who worked with your father. Talk to his close friends and colleagues
- they might know more.”