\chapter{}

\lettrine{I}{t had} been a few days since Divya moved into Aryan's forest 
house. Initially, she found it difficult to adjust to the natural surroundings
with minimal amenities, but eventually, she got used to living alone in the
forest. She had to do much more physical work than in the city, but all those
efforts helped her remain fit and agile. She felt more active and energetic
in her new house than in any air-conditioned room she had lived in. She wondered
if humans were ever designed to live in comfortable houses and follow a
sedentary lifestyle.

One day, while having lunch that she had prepared, Aryan said, “I think we need
to plan our next attack.”

“Do you have a plan?” Divya asked. “The minister is not going to visit
Tirupati again for a while.”

“Yes, but he will be in Chennai next month. Elections are around the corner, and
he has a busy campaign schedule in the city”

“Chennai is quite close—just 160 km from here”

“Yes. He will be starting his election campaign by throwing a party
for a few influential people at his guest house located on the outskirts of the
city. I have located the place on Google Maps, but I don't know how or from
where we are going to attack. The security cover will be tight, especially in
the wake of our recent attacks”, Aryan wondered.

“It seems like a good opportunity, though. Let's attack him during this party”, Divya
replied firmly. 

“How? We can't stop his car while he's coming in or going out—I am sure security
will escort him from the front and rear. We cannot get into the house with
weapons. In fact, we cannot get anywhere close to his vicinity—they will check
everyone moving in and around. How can we attack him?” Aryan asked doubtfully.

“As I see it, we cannot get within close range or have a direct line of
sight. Is that the problem?”

“Yes, how can we use our bows and arrows to attack him in such a
situation?”

Divya began to explain, “According to the archery training manual, it's not possible. But
archery doesn't always require a line of sight, and archers have attacked their
enemies from far away, even if there was a huge obstacle—like a wall—in
between. That's why it pays to know your history and think a little bit outside
the box. In your case, out of the practice manual.”

Aryan said, “That's impossible. How can you attack somebody from far away, when
there is a large obstacle between you and them? Doesn't that mean you can't
see them and there is no way to take aim? How will you launch the arrows then?
Towards the sky?” he smiled.

Divya replied in a serious tone, “Yes, towards the sky. Think about this—once
you launch an arrow towards the sky, it will travel up for some distance, lose
velocity, and come back towards the earth after a short while—right? Unlike
bullets, which are released with a great force, arrows travel much slower. Hence,
it is possible to estimate where they will fall.”

“So?” Aryan asked, unconvinced.

“If we estimate the angle and force of release of an arrow from a bow, we can
easily determine where it will fall on the earth. And it will fall
with the sharp edge facing towards the earth. That means, even if there is a
huge wall in front of us, we can still strike an enemy standing on the other
side of the wall by adjusting the force and angle of release, provided we know
where he is standing”, Divya said.

Aryan began to recollect the Physics lessons he had in school and the Newton's
laws he had studied.

“What do you propose we do in our case?” Aryan asked.

Divya said, “Simple! We know he is going to be on the terrace along with his
guests. We can position ourselves around 60–80 meters away from the spot and
launch our arrows at a sloping angle, towards the sky. They will go up
initially, gain some distance, and come down to hit our target area after a
short time. But we need to fix the angle of elevation, force of release, and
practice until our delivery is consistent.”

Aryan said, “That is absurd. Madam, please remember that even if we have a clear
line of sight, hitting the target requires a lot of accuracy, force, and
practice. It's easy to miss the target even in such a simple scenario. I think
we should focus on how to get into the line of sight and get a clear view of the
minister so that we can strike right at his heart.”

Divya said, “You just said that the minister, especially in the wake of the
recent attacks, will have many armed security guards around him. Their guns
are faster and far more accurate than our arrows, I guess?”

Aryan nodded in affirmation.

Divya continued, “So, if we get anywhere within their line of sight, the chances
are very good that they will shoot us before we've even launched a single arrow.
Am I wrong?”

Aryan said, “No, you're right. We can't afford to do that.”

Divya said, “In such a situation, getting into their line of sight would only
make it easier for them to kill us. It's almost a suicidal move for us. But
think about this—what advantage do we have that they don't?”

Aryan was silent.

Divya said, “Our arrows may be slower than their bullets, but in this situation,
we are going to convert that disadvantage into an advantage. We are going to
attack from a safe distance and escape from there before they even realize what
happened. We should engage our enemy on our terms and strengths—not theirs.”

Aryan said, “Even if I agree with your suggestion in principle, how can you ensure
accuracy? There is no way you can aim and hit a particular person using this
method.”

Divya said, “Our aim is not to kill the minister right away. The Greeks used
this technique to hurt and intimidate their opposition just before a battle. In
other words, they used archery to mentally weaken their opposition so that their
cavalry and artillery could finish the job. The opposition back then defended
themselves using large shields, but our opposition doesn't have any of that. Our
aim through this campaign should be to create fear in his mind and embarrass him
in front of his guests. We need to shake the ground beneath him so that he
doesn't feel secure anywhere, anytime. People who are afraid will make mistakes.
We will wait and take advantage of it.”

Aryan said, “But there will be other people in the crowd. Our arrows may fall
anywhere on the terrace or even away from it. What if others get killed?”

Divya said, “We will use blunt arrows. People may get hurt, but there will be no
serious wounds.”

Aryan said, “Not bad. We spoil his party, embarrass him before his guests, and
if we're lucky, one of the arrows might even hit and hurt him. We will convey a
clear message to him that his killers are closely watching him and will keep
striking at him wherever he is. That will make him live in constant fear for
his life and will make him think twice before going anywhere outside. He needs to
realize that life is not a commodity to be taken at will. Let's do this.”

Aryan opened Google Maps on his laptop. Since the minister's guest house was
close to the beach, They began to look for an ideal spot, from where they could
launch their arrows. Soon they narrowed down the exact spot.

There were two more houses in front of the minister's house, and then there was
a short lane, followed by the beach. Their chosen location was on the beach,
around 60 m away from the minister's guest house—a distance that was perfect
for their mode of attack.

Over the next few days, they set up a spot on the hills where they could practise
for the attack. They marked an area that covered the same length and breadth as the terrace of the minister's guest house. They setup their bows and arrows at a
distance equal to the distance between the actual target area and their planned
position of attack. They practised the precise angle to hold their bows and the
force with which they had to launch their arrows in order to hit their target area.

Accuracy depended on the angle of elevation of their bow and the distance over which their bowstring was stretched, which determined the force of release. They practised repeatedly
to achieve a fairly consistent result and ensure their arrows fell
somewhere within the marked area.