\chapter{}

\lettrine{A}{bout} five minutes after Aryan and Divya left, Divya got a phone call in her
cell phone.

“Hello . . . What? . . . Yes . . . But . . . OK . . .” was all she spoke. She
disconnected the call.

“Aryan, I need you to drop me at Tirumangalam junction. I'll have to go home,”
Divya told Aryan in a loud voice so that it would be audible amidst the sound of
the bike and the traffic.

“Are you out of your mind? We have to go back to our hideout in the hills by
tonight at any cost. Staying back in Chennai is very risky. Both our lives are
at stake,” Aryan shouted back.

“I . . . My mother needs to be admitted in the hospital immediately and I need
to be there,” Divya said.

“It's dangerous to stay back in this city, Divya. We may get caught anytime,”
Aryan said.

“I need to go, there is no other option,” Divya said.

“OK. I'll drop you there and I'll go back to the hotel. Both of us will leave to
Tirupati tomorrow morning,” Aryan said.

“Right now I don't know how long I need to stay. You go back to the hills. I'll
join you as soon as possible,” Divya said.

Aryan could not convince her not to go home. Divya was as adamant as ever. He
raced to the location she wanted him to drop her and stopped the bike. She got
down and looked at him.

Aryan said, “Come back as soon as possible. Don't use public transport to travel
to Tirupati. Do you have a bike?”

Divya said, “Yes, I have a Scooty.”

Aryan said, “Good. Come back in your Scooty. Also, don't venture out for a long
time in public places. Try to stay inside your house or inside the hospital, as
far as possible.”

“OK. See you soon,” she said and turned to cross the road.

Aryan continued to look at her as she walked away for a few more seconds. He
suddenly felt alone and vulnerable. Divya was more than just a partner in crime
– she was a companion he could rely on. She made him feel confident and
stronger. For the first time, he wished all this was over soon.

He then started his long journey towards Tirupati.