\chapter{}

\lettrine{T}{he cameraman} of the 365×24×7 TV channel, a popular news channel in
India, was broadcasting the minister's speech live, when
the two arrows hit the minister. The minister fell back with a thud. He and
other cameramen caught that moment on their cameras. After a couple of seconds,
he realized what had happened and turned to see where the arrows were being fired
from.  He was in for a shock—more arrows were being released from the terrace of
the old building opposite the lane. He immediately turned his camera towards the
source of the attack and started recording, but he couldn't capture the people
launching them. They were out of focus and had already climbed down before he
could get the focus right.

Arrows had been fired randomly all over the place by someone or maybe more than one
person. As the arrows had stopped, he turned his camera to focus on the crowd, who
were, by then, up on their feet and had almost created a stampede trying to run
away. He rushed forward with his camera to cover injuries. Chairs were scattered
and people were scrambling to run away. Despite panning his camera in all
directions, he couldn't notice any blood or injured people anywhere.

He remembered that the minister was the first to be hit by two arrows directly
and ran towards the stage. By the time he went near the stage, the minister,
with the help of people around him, was already standing on his feet. He zoomed
in the camera to get a clearer view and all he saw was a white shirt and a white
\foreign{veshti}. There was no trace of any blood or injuries anywhere on his
body or clothes. The minister walked out of the venue escorted by the police.

The cameraman once again focused his camera towards the audience—the area was
almost empty. He took a couple of steps forward when he accidentally stepped on
an arrow lying on the ground. He bent down, grabbed the arrow and held it in
front of the camera so that people across the nation could see it. The
arrowhead—the sharp front portion of the arrow—was covered with a small rubber
cap.

He wondered why the attackers took so much effort to launch a sensational attack
in front of the national media if they did not want to cause any injuries. He
got his answer when he looked carefully at the arrow once again. There was a
note wrapped around the stem of the arrow.

He loosened the thread and placed the note in front of the camera so that the
entire nation could read its contents:
\begin{quote}
    We seek justice for our father's murder by this minister, six months ago.
\end{quote}