\chapter{}

\lettrine{A}{ryan} monitored the activities of the minister—the press releases and feature
stories of him in various newspapers and magazines, TV and websites. A simple
Google Alerts in the minister's name sourced all articles, that mentioned his
name, right into Aryan's email inbox. After monitoring his movements and few
visits to the minister's home and office areas, Aryan decided that attacking the
minister in Delhi amidst all the security would be difficult.

There was another obstacle—in Delhi, Aryan's actions will be closely watched,
and it would be easy to trace him. He needed a place where he could live
anonymously, a place that would be difficult to reach for both the thugs and the
police. He wanted a secure base to which he could withdraw, months together if
need be, in order to plan and carry out his attacks. He was sure, more than
one would be required to kill the minister.

Aryan wanted to move out of Delhi both for security, and planning and executing
his attacks—but where could he go? One day, in the newspaper, he came across
an article that mentioned the two annual visits made by the minister to
Tirupati—one on his birthday and the other on his wedding anniversary. Aryan
realized
he had hit his jackpot!

Tirupati is the famous Temple town of South India located in the state of Andhra
Pradesh. The cover of the hills would offer an excellent opportunity to hide and
attack the minister. It would also enable him to build a secure base. The
minister was scheduled to visit Tirupati after a couple of months, on his
birthday. Since it was a personal visit, that too far away from the capital, the
security cover would be minimum. It offered Aryan enough time to establish his
base and plan the attack. It didn't take long for Aryan to zero-in on Tirupati.

Aryan's first stop was UK. He informed people in Delhi that he was shifting to
UK. He hoped this would convince the minister that he was no longer an active
threat. He landed in UK, went to his college and applied for a long leave. He
picked up the best assault archery gear and came back to India—not to Delhi,
but to Chennai. He took a train to Tirupati and checked into a hotel in the
Tirupati town just below the hills.