\chapter{}

The cameraman of the 365 x 24 x 7 TV channel, a popular news channel in India,
was broadcasting the Minister's speech live for the channel viewers when the two
arrows hit the Minister. The Minister fell back with a thud. He and other
cameramen caught that moment on their cameras. After a couple of seconds, he
realized what happened and turned to see where the arrows were being fired from.
He was in for a shock - more arrows were being released from the terrace of the
old building opposite of the lane. He immediately turned his camera towards the
source of the attack and started recording but he couldn't capture the people
launching them. They were standing behind the wall and were out of visibility.

Arrows were fired randomly all over the place by someone or maybe more than one
person. Once the arrows stopped, he turned his camera to focus on the crowd, who
were, by then, up on their feet and had almost created a stampede trying to run
away. He rushed forward with his camera to cover injuries. Chairs were scattered
and people were scrambling to run away. In spite of rotating his camera in all
directions, he couldn't notice any blood or injured people anywhere.

He remembered that the Minister was the first to be hit by two arrows directly
and ran towards the stage. By the time he went near the stage, the Minister,
with the help of people around him, was already standing up on his feet. He
zoomed in the camera to get a clearer view and all he saw was white shirt and
white veshti. There was no trace of any blood or injuries anywhere on his body
or clothes. The Minister walked out of the venue escorted by the police.

The cameraman once again focused his camera towards the audience – the area was
almost empty. He took a couple of steps forward when he accidentally stepped on
an arrow that was lying down. He bent down, grabbed the arrow and held it in
front of the camera so that people across the nation could see it. The arrowhead
(the sharp front portion of the arrow) was covered with a small rubber piece.

He wondered why the attackers took so much pain to launch a sensational attack
in front of the national media if they did not want to cause any injuries. He
got his answer when he looked carefully at the arrow once again. There was a
note wrapped around the stem of the arrow. He loosened the thread and placed the
note in front of the camera so that the entire nation could read its contents -

We seek justice for our father's murder by this Minister, six months back.